---
title: "Group 45 UCSB domestic grad enrollment"
author: "Charlie Wilson"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

#attach relevant packages
library(tidyverse)
library(here)
```

```{r}
#read in UCSB Graduate data
ucsb_grad <- read_csv(here("data", "ucsb_grad_data.csv"))
```

```{r}
#create geom_col of ucsb grad data
ggplot(data = ucsb_grad, aes(y = domestic_enrollment, x = year_abbr, fill = ethnicity)) +
  geom_col(position = "fill") + #change from absolute counts to proportions 
  labs(x = "UCSB grad student class graduation year",
       y = "Percent of UCSB class (%)", 
       title = "Ethnic representation (%) of UCSB graduate students by graduation year") +
       theme_minimal() #change theme
```



**Figure** 1: Ethnic representation of UCSB graduate students as a percentage of the total population of UCSB graduate students. Ethnicity percentages are broken down per graduating class from 2008 - 2019. Pink = "White", light purple = "Unknown", purple = "Other", blue = "Latino", Green/blue = "Filipino, light green = "E. Indian/Pakistan, green = "Chicano", olive green = "Black/African American, orange = "Asian/ Pacific Islander, red = "American Indian/ Alaskan". 
